### 2016-04-28 writing/latex/confut.tex
Add enumerations

\chapter{Conclusions and Future work}
From \ChapterRef{chap:coincs} it is can be seen that automatically classifying
coincidences of mesh patterns is a difficult task, establishing rules for longer
dominating patterns requires many more cases to be taken. It would however
be interesting to consider the self application of the Dominating Rules to mesh
patterns in order to try to capture some of the coincidences described in
\textcite{DBLP:journals/combinatorics/HilmarssonJSVU15} and \textcite{journals/combinatorics/BrandenC11}.

@@

It would be interesting to consider a systematic explanation of Wilf-equivalences
amongst classes where \(\perm{3,2,1}\) is the dominating pattern using the
construction presented in \cite[Sec.~12]{2015arXiv151203226B}, in order to directly
reach enumeration and hopefully establish some of the non-trivial Wilf-equivalences
between classes with different dominating patterns.

>>>>

\chapter{Conclusions and Future work}
From \ChapterRef{chap:coincs} it is can be seen that automatically classifying
coincidences of mesh patterns is a difficult task, establishing rules for longer
dominating patterns requires many more cases to be taken. It would however
be interesting to consider the self application of the  third Dominating Rule to mesh
patterns in order to try to capture some of the coincidences described in
\textcite{DBLP:journals/combinatorics/HilmarssonJSVU15} and \textcite{journals/combinatorics/BrandenC11}.
It is not possible to apply the first and second Dominating Rules to the pattern
itself, since when applying the rules we consider containers of the pattern inside
the avoiders of the dominating pattern. For example if we were to attempt to apply
the first rule to the pattern \(\perm{1,2}\) then we would have to consider
containers of \(\perm{1,2}\) inside \(\av{\perm{1,2}}\), and obviously this can
never occur.

@@

It would be interesting to consider a systematic explanation of Wilf-equivalences
amongst classes where \(\perm{3,2,1}\) is the dominating pattern using the
construction presented in \cite[Sec.~12]{2015arXiv151203226B}, in order to directly
reach enumeration and hopefully establish some of the non-trivial Wilf-equivalences
between classes with different dominating patterns. It is possible to show that
the sets consisting of \textpattern{}{1,2}{1/2,2/0,0/0,1/0,1/1,2/1} and
\(\perm{2,3,1}\), or \(\perm{3,2,1}\), are Wilf-equivalent.

### 2016-04-28 writing/latex/wilf.tex
Getting closer
Add enumerations

\chapter{Wilf-equivalences under dominating  patterns}

@@

Evauluation of this generating function gives the Fine numbers
(\href{https://oeis.org/A000957}{OEIS: A000957}). This pattern is one of the
quadrant marked mesh patterns studied by Remmel, Kitaev and TiefenbruckZ\cite{2012arXiv1201.6243K}.

@@

Now consider \(p_4 = \textpattern{}{1}{0/0,0/1,1/0}\), the avoiders of this
pattern are permutations that do not start with their minimum. In this case we
perform the decomposition around the leftmost element
\begin{equation*}
    \mathcal{\var}_3 =\varepsilon \sqcup \decompleft{0/1,1/0}{\mathcal{C}\setminus\varepsilon}{}{}{\mathcal{C}}
\end{equation*}
All of these classes have the same generating function namely
\begin{equation*}
    \var(x) = 1 + xC(x)(C(x)-1)
\end{equation*}

There is one pattern of length \(1\) still to consider. The pattern
\(p_5 = \textpattern{}{1}{0/0,1/0,1/1}\) is avoided by all permutations
that do not end in their minimum. Considering the standard decomposition
of a \(\perm{2,3,1}\) avoider around the maximum we can see that an avoider
of \(p_5\) must fit into the following form precisely once.
\begin{equation*}
    \mathcal{H} = \varepsilon \sqcup
    \underbrace{\decompmax{0/1,1/0}{\mathcal{C}\setminus\varepsilon}{}{}{\mathcal{C}}}_\text{
        Minimum comes before the maximum.
    } \sqcup
    \underbrace{\decompmax{0/0,0/1,1/0}{}{}{}{\mathcal{H}}}_\text{
        Minimum is after the maximum, cannot be last.
    }
\end{equation*}
Therefore this particular class has generating function \(H(x)\) satisfying
\begin{equation*}
    H(x) = 1 + xC(x)(C(x)-1) + xH(x)
\end{equation*}

@@

Therefore these two patterns have been shown to have the same number of
avoiders of length \(k\) for all \(k\) and therefore all Wilf-equivalent.

@@

Now we must consolidate these two subclasses. In order to do this we must
consider the decomposition around the leftmost point of a permutation in
\(\av{\perm{2,3,1},m_1}\) we gain the following.
\begin{equation*}
    \mathcal{I}_3 = \varepsilon \sqcup
    \decompleft{1/0,0/1}{\mathcal{I}_3}{}{}{\mathcal{G}_3}
\end{equation*}
It is therefore obvious that avoiders of \(m_1\) and avoiders of \(m_4\)
have the same enumeration, and therefore all four patterns are Wilf-equivalent
in \(\av{\perm{2,3,1}}\) with generating function satisfying
\begin{equation*}
    I(x) = 1 + xI(x)G(x)
\end{equation*}

\subsection{}
The classes containing the following patterns are Wilf-equivalent
in \(\av{\perm{2,3,1}}\)
\begin{equation*}
    m_1 = \pattern{}{1,2}{0/0,0/1,0/2,
                    1/0,1/1,1/2,
                    2/0,2/1,2/2}
    \text{ and }
    m_2 = \pattern{}{2,1}{0/0,0/1,0/2,
                    1/0,1/1,1/2,
                    2/0,2/1,2/2}
\end{equation*}
It is obvious that these two are Wilf-equivalent since the only
permutations that contain these patterns are \(\perm{1,2}\) and
\(\perm{2,1}\) respectively, therefore the avoiders of these patterns
are counted by the Catalan numbers at all lengths except for length
\(2\) where there is precisely \(1\) avoider.

@@

Now consider the decomposition around the maximum of a permutation in
\(\av{\perm{2,3,1},m_2}\) This fits into the following set.
\begin{equation*}
    \mathcal{J}_2 = \varepsilon \sqcup
    \decompmax{0/1,1/0}{\mathcal{C}}{}{}{\mathcal{C}\setminus\varepsilon} \sqcup
    \decompmax{0/1,1/0,1/1}{\mathcal{F}}{}{}{}
\end{equation*}
Therefore both of these sets of avoiders are enumerated in the same manner
having generating function satisfying
\begin{equation*}
    J(x) = 1 + xC(x)(C(x)-1) + xF(x)
\end{equation*}

@@

For each of these patterns there is precisely one occurrence
in any permutation containing the pattern. Now consider
the points in the free box in each case. Each of these regions
must contain an avoider of \(\perm{2,3,1}\) that is of length
\(n-2\). Therefore these classes are all Wilf-equivalent
and the number of length \(n\) avoiders is
\begin{equation*}
    K_n = C_n - C_{n-2}
\end{equation*}
for \(n \ge 2\) where \(C_n\) is the \(n\)th Catalan number, the number of
\(\perm{2,3,1}\) avoiders of length \(n\).

\subsection{}
Now consider the containers of the patterns
\begin{equation*}
    \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/2,2/0,2/1,2/2},
    \pattern{}{1,2}{0/0,1/1,0/2,1/0,1/2,2/0,2/1,2/2},
    \pattern{}{1,2}{0/0,0/1,1/1,1/0,1/2,2/0,2/1,2/2}
\end{equation*}
Each of these patterns again occurs precisely once in
any containing permutation. However this time when considering
the free box we need to take into consideration \LemmaRef{lem:incdec}
and so the empty box can only contain a decreasing subsequence. There
is precisely one decreasing subsequence at every length, and so there
is exactly one container of each pattern at each length. The three
patterns are Wilf-equivalent and have \(C_n - 1\) avoiders of
length \(n\) for all \(n \ge 2\).

\subsection{}
The containers of the following patterns can only
have exactly one occurrence.
\begin{equation*}
    \pattern{}{1,2}{0/0,0/1,0/2,1/1,2/0,2/1,2/2}
    \pattern{}{2,1}{0/0,0/1,1/0,1/1,1/2,2/0,2/2}
    \pattern{}{1,2}{0/0,0/1,1/1,1/2,2/0,2/1,2/2}
    \pattern{}{1,2}{0/1,0/2,1/0,1/1,2/0,2/1,2/2}
    \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/2,2/0,2/1}
    \pattern{}{1,2}{0/0,0/1,1/0,1/2,2/0,2/1,2/2}
\end{equation*}
Once again we consider the free boxes, obviously for every pattern
except the first the two boxes are independent, and one contains
any avoider of \(\perm{2,3,1}\) and the other must contain a
decreasing sequence by \LemmaRef{lem:incdec}.
Let us consider the first pattern on it's own. In order to
avoid \(\perm{2,3,1}\) across the free boxes we can add some additional
restrictions
\begin{equation}
    \raisebox{0.6ex}{
    \begin{tikzpicture}[scale=1, baseline=(current bounding box.center)]
        \fill[pattern=north east lines, pattern color=black!75] (1.5, 0) rectangle +(0.5,1);
        \fill[pattern=north east lines, pattern color=black!75] (1.0, 2) rectangle +(0.5,1);
        \draw (1.5,0) -- (1.5,1)
              (1.5,2) -- (1.5,3);
        \modpattern[2]{}{1,2}{0/0,0/1,0/2,1/1,2/0,2/1,2/2}
    \end{tikzpicture}
    }
    \label{eqn:splitboxes}
\end{equation}
Now we can see that the top free box must contain a decreasing sequence,
and the bottom must contain an avoider of \(\perm{2,3,1}\) and these
two do not interact in any manner. The containers of this pattern are counted
the same as the other patterns, and due to this they are Wilf-equivalent.

@@

Now in \(m_2\) and \(m_4\) containers we can use the same method as in
\eqref{eqn:splitboxes} to separate the two decreasing sequences in the
free boxes in the top row, and the mixing happens in the same manner
as in a container of \(m_3\).
We now have that \(m_2,m_3\) and \(m_4\) have the same number of containers
so are Wilf-equivalent, and that \(m_1\) and \(m_2\) have the same generating
function so all four classes are Wilf-equivalent.
\subsection{}
The classes containing the following patterns are Wilf-equivalent
\begin{equation*}
    \pattern{}{1,2}{} \text{ and }
    \pattern{}{2,1}{}
\end{equation*}
This is true since the only avoiders of these patterns are the decreasing
sequence and the increasing sequence respectively, and both of these
avoid \(\perm{2,3,1}\) in all cases. There is therefore \(1\) avoider at
every length.

@@

We need to show that the generating function \(M_3(x)\) is the same as \(M(x)\)
\begin{equation*}
    \begin{aligned}
        M_3(x) &= 1 + xF(x)M_3(x) \\
        &= \frac{1}{1-xF(x)} && \text{Solving for \(M_3(x)\)}\\
        &= \frac{1}{1 - \frac{x}{1+x-xC(x)}} &&\text{Substituting for \(F(x)\)}\\
        &= \frac{1-xC(x) +x}{1-xC(x)}\\
        &= 1+xC(x)
    \end{aligned}
\end{equation*}
We have that \(M_3(x) = 1+xC(x)= M(x) \) so all four patterns are Wilf-equivalent.

@@

Now we solve \EquationRef{eqn:ngen} for \(N_1(x)\)
\begin{equation}
    \begin{aligned}
        N_1(x)&= 1+x(N_1(x)-1)C(x)+xF(x)\\
        &= 1+xN_1(x)C(x)-xC(x)+\frac{x}{1+x-xC(x)} &&\text{Substitution of \(F(x)\)}\\
        N_1(x)(1-xC(x))&= \frac{x^2C^2(x) - (x^2+2x)C(x) + 2x+1}{1+x-xC(x)}\\
        N_1(x) &= \frac{x^2C^2(x) - (x^2+2x)C(x) + x+1+x}{x^2C^2(x) - (x^2+2x)C(x) +x+1}\\
        &= 1 +\frac{x}{x^2C^2(x) - (x^2+2x)C(x) +x+1}\\
        &= 1 + \frac{x}{1-x^2C(x)-xC(x)} && xC^2(x) = C(x)-1\\
        &= 1 + \frac{xC^2(x)}{C^2(x) - xC^3(x)(x+1)}\\
        &= 1 + \frac{xC^2(x)}{C(x) - xC^2(x) + xC(x)} && xC^2(x) = C(x)-1\\
        N_1(x)&= 1 + \frac{xC^2(x)}{1+xC(x)} && C(x) = 1+xC^2(x)\\
    \end{aligned}
\end{equation}
We have shown that \(N_1\) and \(N_4\) are indeed the same generating function,
and we have that the classes containing these four patterns are Wilf-equivalent.

@@

This gives us a generating function \(P(x)\) satisfying
\begin{align}
    P(x) &= 1 + xP(x)P^\prime(x) \label{eqn:Pgen}\\
    P(x) &= 1 + x(P(x)-1)P^\prime(x)\label{eqn:PprimeGen}
\end{align}

Solving \EquationRef{eqn:PprimeGen} for \(P^\prime(x)\) and substituting into
\EquationRef{eqn:Pgen} gives us the fact that a the generating function for
\(P(x)\) satisfies
\begin{equation}
    P(x) = xP^2(x) - x(P(x) - 1) + 1
\end{equation}

\subsection{}
\begin{gather*}
        \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,1/2,2/2},
        \pattern{}{1,2}{0/1,0/2,1/0,1/1,1/2,2/0,2/2},
        \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,1/2,2/1},
        \pattern{}{2,1}{0/0,0/1,0/2,1/1,1/2,2/0,2/1},
        \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,1/2,2/0},\\
        \pattern{}{1,2}{0/0,0/1,0/2,1/2,2/0,2/1,2/2},
        \pattern{}{1,2}{0/0,0/1,0/2,1/1,1/2,2/0,2/2},
        \pattern{}{1,2}{0/0,0/1,1/0,1/1,1/2,2/0,2/1},
        \pattern{}{1,2}{0/0,0/1,1/0,1/1,1/2,2/0,2/1}
\end{gather*}

@@

Now decompose an avoider of \textpattern{}{1,2}{0/0,0/1,1/0,1/1,1/2,2/0,2/1}
around the leftmost point.
\begin{equation*}
    \mathcal{Q}_3 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\scriptstyle \mathcal{Q}\setminus\varepsilon}{}{}{\mathcal{C}}
    \sqcup \decompleft{0/0,0/1,1/0}{}{}{}{\mathcal{G}_3}
\end{equation*}
This gives generating function \(Q_3(x)\) satisfying
\begin{equation*}
    \begin{aligned}
        Q(x) &= 1 +xC(x)(P(x)-1) + xG(x)\\
        &= C(x) - xC^2(x) + xC(x) +x^2C^3(x) - x^2C^2 && \text{Solving for \(Q(x)\)}\\
        &= 1 + xC(x) +x^2C^3(x)-xC^2(x) && C = 1+xC^2(x)\\
        &= 1 + x + x^2C^3(x) && xC^2(x) = C(x)-1\\
        &= 1 + x + xC(x)(C(x)-1)
    \end{aligned}
\end{equation*}
This is equivalent to \EquationRef{eq:qgen}, and therefore
the classes containing all of these patterns are Wilf-equivalent.

>>>>

\chapter[Wilf-Classification]{Wilf-equivalences under dominating  patterns}

@@

Evauluation of this generating function gives a the Fine numbers
(\href{https://oeis.org/A000957}{OEIS: A000957}).
\begin{equation*}
    1, 0, 1, 2, 6, 18, 57, 186, 622, 2120, 7338,\dotsc
\end{equation*}
This pattern is one of the
quadrant marked mesh patterns studied by Remmel, Kitaev and Tiefenbruck\cite{2012arXiv1201.6243K}.

@@

Now consider \(p_4 = \textpattern{}{1}{0/0,0/1,1/0}\), the avoiders of this
pattern are permutations that do not start with their minimum. In this case we
perform the decomposition around the leftmost element
\begin{equation*}
    \mathcal{\var}_3 =\varepsilon \sqcup \decompleft{0/1,1/0}{\mathcal{C}\setminus\varepsilon}{}{}{\mathcal{C}}
\end{equation*}
All of these classes have the same generating function namely
\begin{equation*}
    \var(x) = 1 + xC(x)(C(x)-1)
\end{equation*}
Enumeration of this generating function gives
\begin{equation*}
    1, 0, 1, 3, 9, 28, 90, 297, 1001, 3432, 11934,\dotsc
\end{equation*}

There is one pattern of length \(1\) still to consider. The pattern
\(p_5 = \textpattern{}{1}{0/0,1/0,1/1}\) is avoided by all permutations
that do not end in their minimum. Considering the standard decomposition
of a \(\perm{2,3,1}\) avoider around the maximum we can see that an avoider
of \(p_5\) must fit into the following form precisely once.
\begin{equation*}
    \mathcal{H} = \varepsilon \sqcup
    \underbrace{\decompmax{0/1,1/0}{\mathcal{C}\setminus\varepsilon}{}{}{\mathcal{C}}}_\text{
        Minimum comes before the maximum.
    } \sqcup
    \underbrace{\decompmax{0/0,0/1,1/0}{}{}{}{\mathcal{H}}}_\text{
        Minimum is after the maximum, cannot be last.
    }
\end{equation*}
Therefore this particular class has generating function \(H(x)\) satisfying
\begin{equation*}
    H(x) = 1 + xC(x)(C(x)-1) + x(H(x)-1)
\end{equation*}
This generating function can be enumerated to give
\begin{equation*}
    	1, 0, 1, 4, 13, 41, 131, 428, 1429, 4861, 16795,\dotsc
\end{equation*}

@@

Therefore these two patterns have been shown to have the same number of
avoiders of length \(k\) for all \(k\) and therefore all Wilf-equivalent.
The avoiders have enumeration
\begin{equation*}
    1, 1, 1, 3, 11, 38, 127, 423, 1423, 4854, 16787,\dotsc
\end{equation*}

@@

Now we must consolidate these two subclasses. In order to do this we must
consider the decomposition around the leftmost point of a permutation in
\(\av{\perm{2,3,1},m_1}\) we gain the following.
\begin{equation*}
    \mathcal{I}_3 = \varepsilon \sqcup
    \decompleft{1/0,0/1}{\mathcal{I}_3}{}{}{\mathcal{G}_3}
\end{equation*}
It is therefore obvious that avoiders of \(m_1\) and avoiders of \(m_4\)
have the same enumeration, and therefore all four patterns are Wilf-equivalent
in \(\av{\perm{2,3,1}}\) with generating function satisfying
\begin{equation*}
    I(x) = 1 + xI(x)G(x)
\end{equation*}
This can be enumerated to give the sequence
\begin{equation*}
    1, 1, 1, 2, 6, 19, 61, 200, 670, 2286, 7918,\dotsc
\end{equation*}
This corresponds to OEIS sequence number \href{https://oeis.org/A035929}{A035929}
with offset 1.

\subsection{}
The classes containing the following patterns are Wilf-equivalent
in \(\av{\perm{2,3,1}}\)
\begin{equation*}
    m_1 = \pattern{}{1,2}{0/0,0/1,0/2,
                    1/0,1/1,1/2,
                    2/0,2/1,2/2}
    \text{ and }
    m_2 = \pattern{}{2,1}{0/0,0/1,0/2,
                    1/0,1/1,1/2,
                    2/0,2/1,2/2}
\end{equation*}
It is obvious that these two are Wilf-equivalent since the only
permutations that contain these patterns are \(\perm{1,2}\) and
\(\perm{2,1}\) respectively, therefore the avoiders of these patterns
are counted by the Catalan numbers at all lengths except for length
\(2\) where there is precisely \(1\) avoider.
Therefore there are
\begin{equation*}
    1, 1, 1, 5, 14, 42, 132, 429, 1430, 4862, 16796,\cdots
\end{equation*}

@@

Now consider the decomposition around the maximum of a permutation in
\(\av{\perm{2,3,1},m_2}\) This fits into the following set.
\begin{equation*}
    \mathcal{J}_2 = \varepsilon \sqcup
    \decompmax{0/1,1/0}{\mathcal{C}}{}{}{\mathcal{C}\setminus\varepsilon} \sqcup
    \decompmax{0/1,1/0,1/1}{\mathcal{F}}{}{}{}
\end{equation*}
Therefore both of these sets of avoiders are enumerated in the same manner
having generating function satisfying
\begin{equation*}
    J(x) = 1 + xC(x)(C(x)-1) + xF(x)
\end{equation*}
This generating function gives
\begin{equation*}
    1, 1, 1, 4, 11, 34, 108, 354, 1187, 4054, 14054,\dotsc
\end{equation*}

@@

For each of these patterns there is precisely one occurrence
in any permutation containing the pattern. Now consider
the points in the free box in each case. Each of these regions
must contain an avoider of \(\perm{2,3,1}\) that is of length
\(n-2\). Therefore these classes are all Wilf-equivalent
and the number of length \(n\) avoiders is
\begin{equation*}
    K_n = C_n - C_{n-2}
\end{equation*}
for \(n \ge 2\) where \(C_n\) is the \(n\)th Catalan number, the number of
\(\perm{2,3,1}\) avoiders of length \(n\). This gives the sequence
\begin{equation*}
    1, 1, 1, 4, 12, 37, 118, 387, 1298, 4433, 15366,\dotsc
\end{equation*}

\subsection{}
Now consider the containers of the patterns
\begin{equation*}
    \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/2,2/0,2/1,2/2},
    \pattern{}{1,2}{0/0,1/1,0/2,1/0,1/2,2/0,2/1,2/2},
    \pattern{}{1,2}{0/0,0/1,1/1,1/0,1/2,2/0,2/1,2/2}
\end{equation*}
Each of these patterns again occurs precisely once in
any containing permutation. However this time when considering
the free box we need to take into consideration \LemmaRef{lem:incdec}
and so the empty box can only contain a decreasing subsequence. There
is precisely one decreasing subsequence at every length, and so there
is exactly one container of each pattern at each length. The three
patterns are Wilf-equivalent and have \(C_n - 1\) avoiders of
length \(n\) for all \(n \ge 2\).
This gives the sequence
\begin{equation*}
    1, 1, 1, 4, 13, 41, 131, 428, 1429, 4861, 16795,\dotsc\tag{\href{https://oeis.org/A001453}{OEIS: A001453} offset 2}
\end{equation*}

\subsection{}
The containers of the following patterns can only
have exactly one occurrence.
\begin{equation*}
    \pattern{}{1,2}{0/0,0/1,0/2,1/1,2/0,2/1,2/2}
    \pattern{}{2,1}{0/0,0/1,1/0,1/1,1/2,2/0,2/2}
    \pattern{}{1,2}{0/0,0/1,1/1,1/2,2/0,2/1,2/2}
    \pattern{}{1,2}{0/1,0/2,1/0,1/1,2/0,2/1,2/2}
    \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/2,2/0,2/1}
    \pattern{}{1,2}{0/0,0/1,1/0,1/2,2/0,2/1,2/2}
\end{equation*}
Once again we consider the free boxes, obviously for every pattern
except the first the two boxes are independent, and one contains
any avoider of \(\perm{2,3,1}\) and the other must contain a
decreasing sequence by \LemmaRef{lem:incdec}.
Let us consider the first pattern on it's own. In order to
avoid \(\perm{2,3,1}\) across the free boxes we can add some additional
restrictions
\begin{equation}
    \raisebox{0.6ex}{
    \begin{tikzpicture}[scale=1, baseline=(current bounding box.center)]
        \fill[pattern=north east lines, pattern color=black!75] (1.5, 0) rectangle +(0.5,1);
        \fill[pattern=north east lines, pattern color=black!75] (1.0, 2) rectangle +(0.5,1);
        \draw (1.5,0) -- (1.5,1)
              (1.5,2) -- (1.5,3);
        \modpattern[2]{}{1,2}{0/0,0/1,0/2,1/1,2/0,2/1,2/2}
    \end{tikzpicture}
    }
    \label{eqn:splitboxes}
\end{equation}
Now we can see that the top free box must contain a decreasing sequence,
and the bottom must contain an avoider of \(\perm{2,3,1}\) and these
two do not interact in any manner. The containers of this pattern are counted
the same as the other patterns, and due to this they are Wilf-equivalent. The containers
have generating function \(\frac{x^2C(x)}{(1-x)}\). Enumerating avoiders
therefore gives us
\begin{equation*}
    1, 1, 1, 3, 10, 33, 109, 364, 1233, 4236, 14740,\dotsc
\end{equation*}

@@

Now in \(m_2\) and \(m_4\) containers we can use the same method as in
\eqref{eqn:splitboxes} to separate the two decreasing sequences in the
free boxes in the top row, and the mixing happens in the same manner
as in a container of \(m_3\).
We now have that \(m_2,m_3\) and \(m_4\) have the same number of containers
so are Wilf-equivalent, and that \(m_1\) and \(m_2\) have the same generating
function so all four classes are Wilf-equivalent.

Evaluating the generating function \(L(x)\) gives us the enumeration
\begin{equation*}
    1, 1, 1, 2, 6, 20, 68, 233, 805, 2807, 9879,\dotsc
\end{equation*}

\subsection{}
The classes containing the following patterns are Wilf-equivalent
\begin{equation*}
    \pattern{}{1,2}{} \text{ and }
    \pattern{}{2,1}{}
\end{equation*}
This is true since the only avoiders of these patterns are the decreasing
sequence and the increasing sequence respectively, and both of these
avoid \(\perm{2,3,1}\) in all cases. There is therefore \(1\) avoider at
every length.

@@

We need to show that the generating function \(M_3(x)\) is the same as \(M(x)\)
\begin{equation*}
    \begin{aligned}
        M_3(x) &= 1 + xF(x)M_3(x) \\
        &= \frac{1}{1-xF(x)} && \text{Solving for \(M_3(x)\)}\\
        &= \frac{1}{1 - \frac{x}{1+x-xC(x)}} &&\text{Substituting for \(F(x)\)}\\
        &= \frac{1-xC(x) +x}{1-xC(x)}\\
        &= 1+xC(x)
    \end{aligned}
\end{equation*}
We have that \(M_3(x) = 1+xC(x)= M(x) \) so all four patterns are Wilf-equivalent
 and have enumeration sequence
 \begin{equation*}
     1, 1, 1, 2, 5, 14, 42, 132, 429, 1430, 4862,\dotsc
 \end{equation*}
 This is an offset of the Catalan numbers.

@@

Now we solve \EquationRef{eqn:ngen} for \(N_1(x)\)
\begin{equation}
    \begin{aligned}
        N_1(x)&= 1+x(N_1(x)-1)C(x)+xF(x)\\
        &= 1+xN_1(x)C(x)-xC(x)+\frac{x}{1+x-xC(x)} &&\text{Substitution of \(F(x)\)}\\
        N_1(x)(1-xC(x))&= \frac{x^2C^2(x) - (x^2+2x)C(x) + 2x+1}{1+x-xC(x)}\\
        N_1(x) &= \frac{x^2C^2(x) - (x^2+2x)C(x) + x+1+x}{x^2C^2(x) - (x^2+2x)C(x) +x+1}\\
        &= 1 +\frac{x}{x^2C^2(x) - (x^2+2x)C(x) +x+1}\\
        &= 1 + \frac{x}{1-x^2C(x)-xC(x)} && xC^2(x) = C(x)-1\\
        &= 1 + \frac{xC^2(x)}{C^2(x) - xC^3(x)(x+1)}\\
        &= 1 + \frac{xC^2(x)}{C(x) - xC^2(x) + xC(x)} && xC^2(x) = C(x)-1\\
        N_1(x)&= 1 + \frac{xC^2(x)}{1+xC(x)} && C(x) = 1+xC^2(x)\\
    \end{aligned}
\end{equation}
We have shown that \(N_1\) and \(N_4\) are indeed the same generating function,
and we have that the classes containing these four patterns are Wilf-equivalent.
Evaluating the generating function \(N(x)\) gives
\begin{equation*}
    1, 1, 1, 3, 8, 24, 75, 243, 808, 2742, 9458,\dotsc \tag{\href{https://oeis.org/A001453}{OEIS: A001453}}
\end{equation*}

@@

This gives us a generating function \(P(x)\) satisfying
\begin{align}
    P(x) &= 1 + xP(x)P^\prime(x) \label{eqn:Pgen}\\
    P^\prime(x) &= 1 + x(P(x)-1)P^\prime(x)\label{eqn:PprimeGen}
\end{align}

Solving \EquationRef{eqn:PprimeGen} for \(P^\prime(x)\) and substituting into
\EquationRef{eqn:Pgen} gives us the fact that a the generating function for
\(P(x)\) satisfies
\begin{equation}
    P(x) = xP^2(x) - x(P(x) - 1) + 1
\end{equation}
Evaluating \(P(x)\) gives us the sequence
\begin{equation*}
    1, 1, 1, 2, 4, 9, 21, 51, 127, 323, 835,\dotsc
\end{equation*}
This is an offset of the Motzkin numbers \href{https://oeis.org/A001006}{(OEIS: A001006)}.
\subsection{}
\begin{gather*}
        \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,1/2,2/2},
        \pattern{}{1,2}{0/1,0/2,1/0,1/1,1/2,2/0,2/2},
        \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,1/2,2/1},
        \pattern{}{2,1}{0/0,0/1,0/2,1/1,1/2,2/0,2/1},
        \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,1/2,2/0},\\
        \pattern{}{1,2}{0/0,0/1,0/2,1/2,2/0,2/1,2/2},
        \pattern{}{1,2}{0/0,0/1,0/2,1/1,1/2,2/0,2/2},
        \pattern{}{1,2}{0/0,0/1,1/0,1/1,1/2,2/0,2/1},
        \pattern{}{1,2}{0/0,0/1,1/0,1/1,1/2,2/0,2/1}
\end{gather*}

@@

Now decompose an avoider of \textpattern{}{1,2}{0/0,0/1,1/0,1/1,1/2,2/0,2/1}
around the leftmost point.
\begin{equation*}
    \mathcal{Q}_3 = \varepsilon \sqcup
    \decompleft{0/1,1/0}{\scriptstyle \mathcal{Q}\setminus\varepsilon}{}{}{\mathcal{C}}
    \sqcup \decompleft{0/0,0/1,1/0}{}{}{}{\mathcal{G}_3}
\end{equation*}
This gives generating function \(Q_3(x)\) satisfying
\begin{equation*}
    \begin{aligned}
        Q(x) &= 1 +xC(x)(P(x)-1) + xG(x)\\
        &= C(x) - xC^2(x) + xC(x) +x^2C^3(x) - x^2C^2 && \text{Solving for \(Q(x)\)}\\
        &= 1 + xC(x) +x^2C^3(x)-xC^2(x) && C = 1+xC^2(x)\\
        &= 1 + x + x^2C^3(x) && xC^2(x) = C(x)-1\\
        &= 1 + x + xC(x)(C(x)-1)
    \end{aligned}
\end{equation*}
This is equivalent to \EquationRef{eq:qgen}, and therefore
the classes containing all of these patterns are Wilf-equivalent.
The classes have enumeration
\begin{equation*}
    1, 1, 1, 3, 9, 28, 90, 297, 1001, 3432, 11934,\dotsc
\end{equation*}
This is an offset of OEIS Sequence number \href{http://oeis.org/A071724}{A071724}.
